Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2015-05-13 response.txt

We clarify our discussion of the uniform screen model in the
Introduction. k(lambda) is an empirical equation; predictions of
attenuation values from k(lambda) do assume a dust distribution.

* First paragraph of Sect. 2.2.3. The K98 IR estimator actually assumes
that the galaxy is totally buried into dust. Therefore, combining the UV
with the TIR directly can be a dangerous game (though quite common in
the literature). As UV is detected, galaxies are not that strongly
attenuated so the assumption does not hold and the dust heating sources
are not the same anymore, which in turn should change the calibration
coefficient. Also, the listed assumptions are not enough in my opinion.
Even if the SFR is constant over 10^8 years, the Halpha and UV+IR SFR
would not be the same, because of contamination by stars older than 100
Myr in the UV but not in Halpha. As possible biases in the derivation of
the SFR would have a direct impact on the results, I suggest that they
are fully taken into account and properly discussed in the paper. In any
case, beyond that, assuming in effect that SFR(Halpha)=SFR(UV+TIR) is a
very strong assumption. If there is a tiny wiggle of the SFR in the last
few Myr, that is sufficient to throw the different SFR completely off
from one another. As said just above, the results of this paper are
sensitive to such effects. I think it is therefore especially important
that the impact of such variations is discussed in more detail than in a
lone paragraph in Section 4.

We agree that determinations of star formation rates are fraught with
uncertainty. Attenuation does not have to decrease with increasing UV
emission: galaxies may have one set of star forming regions which are
totally buried and another set which are totally exposed.  Many papers
discuss in much detail the assumptions made by those who convert
luminosity to star formation rate.  K98 and the review article by Madau
& Dickinson, which we cite in section 4, mention many of these same
issues.

Fig. 2b of Madau & Dickinson 2014 shows negligible contamination to the
UV luminosity from stars older than 10^8 Myr which were formed during a
constant SFH.  L_UV/SFR reaches an asymptote, more or less.

We do discuss the pitfalls of assuming that SFR(Halpha)=SFR(UV+IR).  Our
method may not return relations with optimal dispersions.  We warn that
this assumption will be unjustified for individual galaxies.  Thankfully
we have large samples and are interested in average relations.

@@

An extended discussion on our part can be arbitrarily complex---for
example, some in the stellar community might argue that we don't know
even the evolution of the ionizing luminosity of a simple stellar
population (Sana et al. 2012); some in the extragalactic community might
argue that we're extrapolating a total infrared luminosity from two or
three flux densities.  Our assumptions are strong but we do acknowledge
them.  In our view these important details have deserved their own
papers.

* In section 3, I find very odd to present the results in terms of
escape fraction, rather than attenuation as is customary. While
technically they are equivalent quantities, I find that using escape
fractions is detrimental to the clarity of the paper. I would strongly
suggest to switch to attenuations.

We believe that magnitudes are strange metrics.  A(Ha) = 2.5 is
deceptive at a glance since we mean to write that we see only 10% of the
intrinsic luminosity.  We have tried to write this paper for an audience
comprising novices.

@@

* Last paragraph of the conclusion. I doubt ALMA will be used to provide
direct test of the "uniform screen assumption". Not that it cannot, but
rather this assumption is known to be invalid for most practical
purposes. There is an enormous quantity of archival observations
available for numerous instruments showing the beautifully complex
interplay between stars and dust in the Milky and in nearby galaxies.

We clarify that ALMA will be a boon to high-redshift galaxies.

* Finally, some general comments. The differential reddening is not
mentioned in the paper even though that is what the authors aim at
studying. In her last attenuation law papers, Calzetti defines the
difference of the attenuation between the stars and the gas in terms of
differential reddening rather than in terms of escape ratios (that is,
E(B-V)stars=0.44*E(B-V)gas rather than AVstars=0.44*AVgas). This is an
important difference as Rv is different between the starburst law
(Rv=4.05) and the Milky Way law (Rv=3.1). If I remember correctly, that
can make a noticeable difference when computing A(Halpha)/A(FUV).

We hope our language clarifies this point.  When we discuss whether
high-redshift galaxies obey or disobey the Calzetti attenuation formula,
we include Rv in our definition of the attenuation formula, k(lambda).
We are only interested in the E(B-V) relations if we believe the
Calzetti formula applies to high-redshift dusty galaxies.  (In short, we
do not aim to study the differential reddening.)

@@

* The title of Sect. 3.1 is unclear. One would wonder what "relation" is
considered here.

Clarified.

* Sect. 3.1, it would be useful to specify what exactly is the "low
redshift IRX-beta relation".

Our subsequent sentences explain the IRX-beta relation: the UV escape
fraction is a function of IRX and an attenuation formula relates the
escape fraction to beta.

### 2015-05-13 paper.tex
Final changes

The uniform screen assumption is unrealistic.  A low-redshift galaxy with a
high emergent UV luminosity and a low IR luminosity---a dust-poor
galaxy---suffers a low amount of UV attenuation.  The \citet{calzetti00} formula
predicts how much H$\alpha$ attenuation it should suffer; the prediction
underestimates the measured H$\alpha$ attenuation.  The galaxy's regions with
$>10$ M$_{\odot}$ stars, which ionize gas, have more dust than its regions
with less massive stars that emit in the UV and leave the gas unionized
\citep{calzetti94,calzetti97b}.  While the discrepancy in amounts of dust does
not invalidate the screen part of our assumption, it does invalidate the
uniform part.

@@

The discrepancy between the uniform assumption and real dust
distributions in low-redshift dust-poor galaxies grows even larger if we
consider that galaxies have centers and outskirts---that galaxies are not
point sources.  A number of studies find
that H$\alpha$ and UV attenuation decrease with increasing radius
\citep{boissier04,prescott07,munoz09}.  Ionizing stars are surrounded by more
dust than nonionizing UV-emitting stars; ionizing stars
at large radii have less dust than ionizing stars at small radii, and similarly
for nonionizing UV-emitting stars.

We know little about dust distributions in low-redshift dusty galaxies, which
have high IR luminosities and low-to-high emergent UV luminosities.  Their
IR emitting regions span a range of sizes, from sub- to several kpc
\citep{diaz10}.  Measuring a size is hard enough; imaging a distribution is
even harder.  If a dusty galaxy's measured H$\alpha$ attenuation agreed with
the prediction from the \citet{calzetti00} attenuation formula, we might
conclude that the galaxy has a uniform dust distribution only if we believe
that the prediction is valid.  If a dusty galaxy's measured H$\alpha$
attenuation disagreed with the prediction from the \citet{calzetti00}
formula, the galaxy might have a nonuniform dust distribution, like that of a
dust-poor galaxy.  This explanation for the disagreement is not unique.  The
galaxy might have a uniform distribution and obey a different $k(\lambda)$.

@@

In this paper, we ask the question, For dusty galaxies at $z \sim 0$ and
$z \sim 1$, how does H$\alpha$ attenuation relate to the prediction made by
the \citet{calzetti00} attenuation formula?  We: (1) show that H$\alpha$
attenuation differs from
the prediction; (2) show that the relations between H$\alpha$ and UV
attenuation differ from the relation for low-redshift dust-poor galaxies; and
(3) argue that an interpretation in the context of dust distributions relies on
the shaky assumption that the \citet{calzetti00} attenuation formula is
universally valid.

%This paper is organized as follows.  We present the data and derived quantities
%in \S\ref{sec:data}.  The relation is in \S\ref{sec:results}.  Our argument is
%in \S\ref{sec:discuss}.  We conclude in \S\ref{sec:conclude}.
For this paper we assume a cosmology with $H_{0} = 70$ km s$^{-1}$ Mpc $^{-1}$,
$\Omega_{\mathrm{m}} = 0.3$, and $\Omega_{\Lambda} = 0.7$.  Our terminology
is: (1) a \emph{uniform} screen is a screen equally thick between a region with
stars which ionize gas and a region with stars which emit in the UV and do not
ionize gas; (2) a \emph{dust-poor} galaxy is selected from a UV image and
generally has low values of UV and H$\alpha$ attenuation; and (3) a \emph{dusty}
galaxy is selected from an IR image and generally has high values of UV and
H$\alpha$ attenuation.  The samples of dust-poor and dusty galaxies are not
dichotomous.  More details are in the following section.

@@

We use IR, emergent UV, and H$\alpha$ luminosities to determine attenuation by
dust.  In this section we detail our catalogs and samples.

@@

We use a nonstandard method to determine H$\alpha$ attenuation, so we test this
method first for low-redshift dust-poor galaxies which have known dust
properties.  We choose a sample of star-forming galaxies at $z \sim 0$ that are
analogs of common star-forming galaxies at high redshift
\citep[LBAs;][]{overzier09,overzier11}.

@@

\bibitem[Calzetti(1997b)]{calzetti97b} Calzetti, D.\ 1997, American 
Institute of Physics Conference Series, 408, 403

\bibitem[Calzetti(1997a)]{calzetti97a} Calzetti, D.\ 1997, \aj, 113, 162

>>>>

The uniform screen assumption is unrealistic.  A low-redshift galaxy with a
high emergent UV luminosity and a low IR luminosity---a dust-poor
galaxy---has a high UV escape fraction.  The \citet{calzetti00} formula
predicts its H$\alpha$ escape fraction; the prediction
overestimates the measured H$\alpha$ escape fraction.  The galaxy's regions with
$>10$ M$_{\odot}$ stars, which ionize gas, have more dust than its regions
with less massive stars that emit in the UV and leave the gas unionized
\citep{calzetti94,calzetti97b}.  While the discrepancy in amounts of dust does
not invalidate the screen part of our assumption, it does invalidate the
uniform part.

@@

The discrepancy between the uniform assumption and real dust
distributions in low-redshift dust-poor galaxies grows even larger if we
consider that galaxies have centers and outskirts---that galaxies are not
point sources.  A number of studies find
that H$\alpha$ and UV escape fractions increase with increasing radius
\citep{boissier04,prescott07,munoz09}.  Ionizing stars are surrounded by more
dust than nonionizing UV-emitting stars; ionizing stars
at large radii have less dust than ionizing stars at small radii, and similarly
for nonionizing UV-emitting stars.

We know little about dust distributions in low-redshift dusty galaxies, which
have high IR luminosities and low-to-high emergent UV luminosities.  Their
IR emitting regions span a range of sizes, from sub- to several kpc
\citep{diaz10}.  Measuring a size is hard enough; imaging a distribution is
even harder.  If a dusty galaxy's measured H$\alpha$ escape fraction agreed with
the prediction from the \citet{calzetti00} attenuation formula, we might
conclude that the galaxy has a uniform dust distribution only if we believe
that the prediction is valid.  If a dusty galaxy's measured H$\alpha$
escape fraction disagreed with the prediction from the \citet{calzetti00}
formula, the galaxy might have a nonuniform dust distribution, like that of a
dust-poor galaxy.  This explanation for the disagreement is not unique.  The
galaxy might have a uniform distribution and obey a different $k(\lambda)$.

@@

In this paper, we ask the question, For dusty galaxies at $z \sim 0$ and
$z \sim 1$, how do H$\alpha$ escape fractions relate to the predictions made by
the \citet{calzetti00} attenuation formula?  We: (1) show that H$\alpha$
escape fractions differ from
the prediction; (2) show that the relations between H$\alpha$ and UV
escape fractions differ from the relation for low-redshift dust-poor galaxies; and
(3) argue that an interpretation in the context of dust distributions relies on
the shaky assumption that the \citet{calzetti00} attenuation formula is
universally valid.

%This paper is organized as follows.  We present the data and derived quantities
%in \S\ref{sec:data}.  The relation is in \S\ref{sec:results}.  Our argument is
%in \S\ref{sec:discuss}.  We conclude in \S\ref{sec:conclude}.
For this paper we assume a cosmology with $H_{0} = 70$ km s$^{-1}$ Mpc $^{-1}$,
$\Omega_{\mathrm{m}} = 0.3$, and $\Omega_{\Lambda} = 0.7$.  Our terminology
is: (1) a \emph{uniform} screen is a screen equally thick between a region with
stars which ionize gas and a region with stars which emit in the UV and do not
ionize gas; (2) a \emph{dust-poor} galaxy generally has high values of UV and
H$\alpha$ escape fractions; and (3) a \emph{dusty} galaxy is selected from an IR
image and generally has low values of UV and H$\alpha$ escape fractions.  The
samples of dust-poor and dusty galaxies are not
dichotomous.  More details are in the following section.

@@

We use IR, emergent UV, and H$\alpha$ luminosities to determine escape
fractions.  In this section we detail our catalogs and samples.

@@

We use a nonstandard method to determine H$\alpha$ escape fractions, so we test this
method first for low-redshift dust-poor galaxies which have known dust
properties.  We choose a sample of star-forming galaxies at $z \sim 0$ that are
analogs of common star-forming galaxies at high redshift
\citep[LBAs;][]{overzier09,overzier11}.

@@

\bibitem[Calzetti(1997b)]{calzetti97b} Calzetti, D.\ 1997b, American 
Institute of Physics Conference Series, 408, 403

\bibitem[Calzetti(1997a)]{calzetti97a} Calzetti, D.\ 1997a, \aj, 113, 162
